Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET

### 2023-12-26 Submission.Rmd
copyedited format
new abstract

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. We build on an oppositional literature positing that *individual differences* matter in our perceptions of characteristics as demands and resources. Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job  characteristics. Procedurally, an exhaustive list of O\*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands. **sentence about lit-implied demands/resources**. **sentence about implications for job design**.

@@

Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

>>>>

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics. O*NET work characteristics were rated by 568 employed respondents. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. These findings have implications for job design.

@@

```{r reproduced, echo=FALSE, fig.cap="LePine's (2022) revised challenge-hindrance stressor framework."}
library(magick)
library(grid)

figure <- image_read("Reproduced_LepineFigure.png")

grid.raster(figure) # works well with margins/etc

Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. The theoretical associations that drive the current study's purpose are presented in Figure \@ref(fig:reproduced), which has been reproduced from @lepine2022challenge.

### 2023-12-26 Submission.tex
new abstract

\abstract{%
Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. We build on an oppositional literature positing that \emph{individual differences} matter in our perceptions of characteristics as demands and resources. Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics. Procedurally, an exhaustive list of O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands. \textbf{sentence about lit-implied demands/resources}. \textbf{sentence about implications for job design}.
}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/reproduced-1.pdf}
\caption{\label{fig:reproduced}LePine (2022) revised challenge-stress-appraisal framework.}
\end{figure}

>>>>

\abstract{%
Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics. O*NET work characteristics were rated by 568 employed respondents. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. These findings have implications for job design.
}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/reproduced-1.pdf}
\caption{\label{fig:reproduced}LePine's (2022) revised challenge-hindrance stressor framework.}
\end{figure}
